Paper notes

### 2019-09-03 paper_notes.Rmd
updates 03_09_2019

f_val <- function(e_w,ew_ng,i_v,S_v){
  if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
    U <- 1
    }else{
      U <- ((1-(round(abs(e_w-ew_ng), digits=2)))/(1-i_v)) * S_v
      }
  round(U,digits = 3)
  }

@@

$$
U^i_e=
\begin{cases}
1, & \text{if} x =  n\times i_e, \\
\\
(\frac{x}{n \times i_e})\times S, & \text{if} \ x < n\times i_e, \\
\\
M + \frac{(1 - \frac{x}{n}) \times (1 - M)}{1 - i_e}, & \text{if} \ x > n\times i_e 
\end{cases}
$$

@@

i_e = 0.5                   # definition of parameters for each function: i_e desired ethnic concentration
M = 0                       # M: right-side slope, S: left-side slope, n = total number of agents in neighborhood
S = 1
n = 8

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S_v <- 1

@@

i_e = 0.6   # parameters to manipulate
S = 1     # Symmetric single-peaked function: S=1,M=0
M = 0     # Linear + Constant function = S=1,M=1
n = 8     # Schelling Threshold function = S=0,M=1

@@

e_w <- 0.5    # parameters to manipulate
i_v <- 0.2    # Symmetric = S:1,M:0/Threshold = S:0
S_v  <- 0
M <-  0

fv0d2 <- f_val(e_w,0,M,i_v,S_v)             # value utility for each option, 
fv1d2 <- f_val(e_w,0.1,M,i_v,S_v)           # increasing nuMber is average ethnic weight of neighborhood j
fv2d2 <- f_val(e_w,0.2,M,i_v,S_v)
fv3d2 <- f_val(e_w,0.3,M,i_v,S_v)
fv4d2 <- f_val(e_w,0.4,M,i_v,S_v)
fv5d2 <- f_val(e_w,0.5,M,i_v,S_v)
fv6d2 <- f_val(e_w,0.6,M,i_v,S_v)
fv7d2 <- f_val(e_w,0.7,M,i_v,S_v)
fv8d2 <- f_val(e_w,0.8,M,i_v,S_v)
fv9d2 <- f_val(e_w,0.9,M,i_v,S_v)
fv10d2 <- f_val(e_w,1.0,M,i_v,S_v)

@@

report_V <- na.omit(data.frame(M,S_v,des_dist,ew_agent,mean_ew_ng,Utility_V))

title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M =", M,"; ", "S = ",S_v)

>>>>

f_val <- function(e_w,ew_ng,i_v,S_v,Mv){
  if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
    U <- 1
    }else{
      U <- ((1-(round(abs(e_w-ew_ng), digits=2)))/(1-i_v)) * S_v
      }
  round(U,digits = 3)
  }

@@

$$
U^i_e=
\begin{cases}
1, & \text{if} \ x =  n\times i_e, \\
\\
(\frac{x}{n \times i_e})\times S, & \text{if} \ x < n\times i_e, \\
\\
M + \frac{(1 - \frac{x}{n}) \times (1 - M)}{1 - i_e}, & \text{if} \ x > n\times i_e 
\end{cases}
$$

@@

i_e = 0.5                   # definition of parameters for each function: i_e desired ethnic concentration
M = 0                       # M: right-side slope, S: left-side slope, n = total number of agents in neighborhood
S = 0
n = 8

@@

e_w <- 0.9
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.0
S_v <- 1

@@

i_e = 0.8  # parameters to manipulate
S = 1     # Symmetric single-peaked function: S=1,M=0
M = 0    # Linear + Constant function = S=1,M=1
n = 4     # Schelling Threshold function = S=0,M=1

@@

e_w <- 0.2    # parameters to manipulate
i_v <- 0.2   # Symmetric = S:1,M:0/Threshold = S:0
S_v  <- 0

fv0d2 <- f_val(e_w,0,i_v,S_v)             # value utility for each option, 
fv1d2 <- f_val(e_w,0.1,i_v,S_v)           # increasing nuMber is average ethnic weight of neighborhood j
fv2d2 <- f_val(e_w,0.2,i_v,S_v)
fv3d2 <- f_val(e_w,0.3,i_v,S_v)
fv4d2 <- f_val(e_w,0.4,i_v,S_v)
fv5d2 <- f_val(e_w,0.5,i_v,S_v)
fv6d2 <- f_val(e_w,0.6,i_v,S_v)
fv7d2 <- f_val(e_w,0.7,i_v,S_v)
fv8d2 <- f_val(e_w,0.8,i_v,S_v)
fv9d2 <- f_val(e_w,0.9,i_v,S_v)
fv10d2 <- f_val(e_w,1.0,i_v,S_v)

@@

report_V <- na.omit(data.frame(S_v,des_dist,ew_agent,mean_ew_ng,Utility_V))

title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r", "S = ",S_v)
